Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-29 manuscript.Rmd
Edits to Results

### Syria as Target
A permutation test for the CRQA of social cohesion and count of all events 
found a statistical difference from chance for DET, NRLINE, maxL, and LAM. 
All other metrics were non-significant (Figure \@ref(fig:plot-rp-targ-all);
\autoref{table-1}). A permutation test for the CRQA of social cohesion and 
count of positive events found no statistical difference from chance for any 
of the metrics other than TT (Figure \@ref(fig:plot-rp-targ-pos); 
\autoref{table-1}). A permutation test for the CRQA of social cohesion and 
count of negative events found a statistical difference from chance for DET, 
NRLINE, L, ENTR, LAM, and TT. All other metrics were non-significant (Figure
\@ref(fig:plot-rp-targ-neg); \autoref{table-1}). Looking at the recurrence 
plots there appears, to be a shift in dynamics around the 36th observation 
which corresponds to May 4th, 2012.

@@

### Syria as Source and Target
A permutation test for the CRQA of social cohesion and count of all events found a statistical difference from chance for DET, NRLINE, and LAM. All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-all); \autoref{table-2}). A permutation test for the CRQA of social cohesion and count of positive events found a statistical difference from chance for maxL, ENTR, and LAM (Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}). A permutation test for the CRQA of social cohesion and count of negative events found a statistical difference from chance for DET, NRLINE, and rENTR. All other metrics were non-significant (Figure \@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}). Looking at the recurrence plots there appears, to be a shift in dynamics around the 36th observation which corresponds to May 4th, 2012.

@@

WCRQA was performed using the crqa package [@R-crqa] for R [@R-base]. Permutation tests
were conducted for each WCRQA to establish upper and lower 95th and 99th percentiles. In
the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and \@ref(fig:plot-wcrqa-source-targ-all)),
the 95th percentiles are represented by horizontal red lines and the 99th percentiles are
represented by horizontal orange lines. The trend lines are plotted in blue.

@@

For social cohesion and count of all events, there is a consistent period 
of above chance recurrence rate from the 7th-12th and 36th-47th window 
(Figure \@ref(fig:plot-wcrqa-targ-all)). Determinism is largely above chance 
from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)). For
social cohesion and count of positive events there is a downward trend in RR 
as the window moves with largly above chance RR from the 1st-18th and 
32nd-45th windows. Determinism was at or above chance for the 8th-17th, 
32nd-34th, and the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)). 
For social cohesion and count of negative events, recurrence rate stays above
or almost above chance from the 4th-7th and 43rd-47th windows, and determinism
is above or nearly above chance in the 1st and 2nd windows, with short intermittent 
peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there is a consistent period of
above or nearly above chance determinism from the 7th-13th and 26th-47th 
windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)). Determinism also 
shows above or nearly above chance values in windows 7th-17th and short, 
intermittent peaks between the 34th and 61st windows (Figure 
\@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion and count of 
positive events, there is a downward trend in RR as the window moves with 
largely above chance values in the first 20 windows and the 32nd-45th windows. 
Determinism stays largely within chance with the exception of windows 13 
through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)). For social cohesion
and negative events, there appears to be an extended time period where RR 
(32nd-47th windows) and DET (35th-39th windows) were above of nearly above 
chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from
May 3rd, 2012 to May 14th, 2012.

>>>>

A permutation test for the CRQA of social cohesion and count of all events 
found a statistical difference from chance for DET, NRLINE, maxL, and LAM. 
All other metrics did not reach significance (Figure \@ref(fig:plot-rp-targ-all);
\autoref{table-1}).

A permutation test for the CRQA of social cohesion and 
count of positive events found no statistically significant difference for any 
of the metrics other than TT (Figure \@ref(fig:plot-rp-targ-pos); 
\autoref{table-1}).

A permutation test for the CRQA of social cohesion and 
count of negative events found a statistically significant difference for DET, 
NRLINE, L, ENTR, LAM, and TT. All other metrics did not reach significance 
(Figure \@ref(fig:plot-rp-targ-neg); \autoref{table-1}).

A qualitative investigation of the recurrence plots suggests
a shift in dynamics around the 36th observation, 
which corresponds to May 4th, 2012.

@@

### Syria as Source and Target
A permutation test for the CRQA of social cohesion and count of all 
events found a statistical difference from chance for DET, NRLINE, and 
LAM. All other metrics were non-significant (Figure 
\@ref(fig:plot-rp-source-targ-all); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of positive 
events found a statistical difference from chance for maxL, ENTR, and LAM 
(Figure \@ref(fig:plot-rp-source-targ-pos); \autoref{table-2}).

A permutation test for the CRQA of social cohesion and count of negative 
events found a statistical difference from chance for DET, NRLINE, and rENTR. 
All other metrics were non-significant (Figure 
\@ref(fig:plot-rp-source-targ-neg); \autoref{table-2}).

Looking qualitatively at the recurrence plots, there again appeared 
to be a shift in dynamics around the 36th observation (May 4th, 2012).

@@

In the plots (see Figures \@ref(fig:plot-wcrqa-targ-all) and 
\@ref(fig:plot-wcrqa-source-targ-all)), the 95th percentiles are represented
by horizontal red lines, and the 99th percentiles are
represented by horizontal orange lines. The trend lines are plotted in blue.

@@

For social cohesion and count of all events, there was a consistent period 
of above-chance RR from the 7th-12th and 36th-47th window 
(Figure \@ref(fig:plot-wcrqa-targ-all)). DET was largely above chance 
from the 46th to the 61st window (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of positive events, there was a downward trend in RR 
as the window moves with largely above-chance RR from the 1st-18th and 
32nd-45th windows. DET was at or above chance for the 8th-17th, 
32nd-34th and at the 60th window (Figure \@ref(fig:plot-wcrqa-targ-all)).

For social cohesion and count of negative events, RR stayed above
or almost above chance from the 4th-7th and 43rd-47th windows. DET
was above or nearly above chance in the 1st and 2nd windows, with intermittent 
peaks in later windows (Figure \@ref(fig:plot-wcrqa-targ-all)).

@@

For social cohesion and count of all events, there was a consistent period of
above- or nearly above-chance DET from the 7th-13th and 26th-47th 
windows (Figure \@ref(fig:plot-wcrqa-source-targ-all)). DET also 
showed above- or nearly above-chance values in windows 7th-17th and 
intermittent peaks between the 34th and 61st windows (Figure 
\@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion and count of 
positive events, there was a downward trend in RR as the window moved, with 
largely above-chance values in the first 20 windows and the 32nd-45th windows. 
DET stayed largely within chance, with the exception of windows 13 
through 19 (Figure \@ref(fig:plot-wcrqa-source-targ-all)).

For social cohesion
and negative events, there was an extended period of time during which RR 
(32nd-47th windows) and DET (35th-39th windows) were above or nearly above 
chance (Figure \@ref(fig:plot-wcrqa-source-targ-all)). These windows span from
May 3rd--14th, 2012.
